---
title: "Fiona's plotly page"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plots for NYC Restaurant Inspection results


### Load packages and data

```{r, message=FALSE,warning=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Take a look at the dataset

```{r}
data("rest_inspec")
```

It is a large dataset with `r nrow(rest_inspec)` observations and `r ncol(rest_inspec)` variables. I am interested in "boro", "cuisine description", "grade", "score", "dba", and "inspection_date" so I will select only these variables, drop missing input, and randomly sample 20000 from them.

### Downsample

```{r}
rest_inspec = 
rest_inspec %>% 
  select(boro, cuisine_description, grade, score, dba, inspection_date) %>% 
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  drop_na() %>% 
  sample_n(20000)

rest_inspec
```

## Plotly Scatterplot

```{r}
scatter_plot =
  rest_inspec %>%
  filter(str_detect(cuisine_description, "[Ff][Rr][Ee][Nn][Cc][Hh]")) %>% 
  mutate(
    text_label = str_c("Grade: ", grade, "\ndba:", dba) 
    ) %>% 
  plot_ly(
    x = ~inspection_date, y = ~score, color = ~boro,
    type = "scatter", mode = "markers",
    alpha = .5, text = ~text_label
    ) %>% 
  layout(title = "The distribution of scores across inspectation dates")

scatter_plot
```

We couldn't observe any clear trend from this scatterplot, indicating that scores have no clear association with the inspection date.

## Plotly boxplot

```{r}
boxplot =
  rest_inspec %>%
  filter(cuisine_description %in% c("French", "Korean", "American", "Asian", "African", "Chinese", "Russian", "Italian")) %>%
  mutate(
    dba = fct_reorder(dba, score)
    ) %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box") %>% 
  layout(title = "The distribution of scores across 8 cuisines")

boxplot
```

We could see that most of the cuisines performed similarily, except for African, Korean, and Russian restaurants.

## Plotly barchart

```{r}
barchart =
  rest_inspec %>% 
  filter(cuisine_description %in% c("French", "Korean", "American", "Asian", "African", "Chinese", "Russian", "Italian")) %>%
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x = ~cuisine_description, y = ~n, color = ~cuisine_description, type = "bar", colors = "viridis") %>% 
  layout(title = "Frequency of 8 cuisines")

barchart
```

We could see that the number of American restaurants was the most, whereas the number of African restaurant is the least. African, Russian, and Korean restaurants had low frequency, might be a explanation for what we observed in the above boxplot for the huge variations in scores.

# Flexdashboard

Please check the [flexdashboard](dashboard.html) I made for these 3 plots.

---
__Quick navigation:__

Return to Fiona's [homepage](index.html)


