---
title: "Fiona's plotly page"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plots for NYC Restaurant Inspection results


### Load packages and data

```{r, message=FALSE,warning=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Take a look at the dataset

```{r}
data("rest_inspec")
```

It is a large dataset with `r nrow(rest_inspec)` observations and `r ncol(rest_inspec)` variables. I am interested in "boro", "cuisine description", "grade", "score", "dba", and "inspection_date" so I will select only these variables, drop missing input, and randomly sample 20000 from them.

### Downsample

```{r}
rest_inspec = 
rest_inspec %>% 
  select(boro, cuisine_description, grade, score, dba, inspection_date) %>% 
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  drop_na() %>% 
  sample_n(20000)

rest_inspec
```

## Plotly Scatterplot

```{r}
scatter_plot =
  rest_inspec %>%
  filter(str_detect(cuisine_description, "[Ff][Rr][Ee][Nn][Cc][Hh]")) %>% 
  mutate(
    text_label = str_c("Grade: ", grade, "\ndba:", dba) 
    ) %>% 
  plot_ly(
    x = ~inspection_date, y = ~score, color = ~boro,
    type = "scatter", mode = "markers",
    alpha = .5, text = ~text_label
    ) %>% 
  layout(
    title = "The distribution of scores across inspectation dates",
    xaxis = list(title = "Inspection date"),
    yaxis = list(title = "Score")
    )

scatter_plot
```

We couldn't observe any clear trend from this scatterplot, indicating that scores does not vary by inspection date.

## Plotly boxplot

```{r}
boxplot =
  rest_inspec %>%
  filter(cuisine_description %in% c("French", "Korean", "American", "Asian", "African", "Chinese", "Russian", "Italian")) %>%
  mutate(
    dba = fct_reorder(dba, score)
    ) %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box") %>% 
  layout(
    title = "The distribution of scores across restaurants of 8 different cuisines",
    xaxis = list(title = "Cuisine of restaurant"),
    yaxis = list(title = "Score")
    )

boxplot
```

We could see that the range of scores for most restaurant cuisines are small and the median score for those restaurants are very close, except for African, Korean, and Russian restaurants. In particular, the range of scores for African restaurants are huge.

## Plotly bar chart

```{r}
barchart =
  rest_inspec %>% 
  filter(cuisine_description %in% c("French", "Korean", "American", "Asian", "African", "Chinese", "Russian", "Italian")) %>%
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x = ~cuisine_description, y = ~n, color = ~cuisine_description, type = "bar", colors = "viridis") %>% 
  layout(
    title = "The frequency counts of restaurants of 8 different cuisines",
    xaxis = list(title = "Cuisine of restaurant"),
    yaxis = list(title = "Frequency counts")
    )

barchart
```

We could see that the frequency counts of American restaurants was the largest (close to 5000), whereas the number of African restaurant is the smallest (nearly 100). African, Russian, and Korean restaurants all had low frequency counts, which might be a explanation for what we observed in the above boxplot for the huge variations in scores for these 3 restaurant cuisines.

# Flexdashboard

Please check the [flexdashboard](dashboard.html) I made for these 3 plots.

---
__Quick navigation:__

Return to Fiona's [homepage](index.html)


